---
title: "p8105_hw1_sc5126.Rmd"
author: "Si Chen"
date: "2023-09-23"
output: github_document
---


## Problem 1

**Load dataset** 
```{r load_data, warning = FALSE, message = FALSE}
library(moderndive)
library(ggplot2)
library(tidyverse)
data("early_january_weather")
```


**Description of the dataset:**\
The variables in the dataset include `r colnames(early_january_weather)`. \
The highest temperature is `r max(early_january_weather$temp)` and the lowest temperature is `r min(early_january_weather$temp)`. The mean of humidity is `r mean(early_january_weather$humid)` and the mean of visibility is `r mean(early_january_weather$visib)`.\
There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns in the dataset.\
The mean temperature is `r mean(early_january_weather$temp)`.\






```{r plot_prob1, message = FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_temp_time.png")
```
As the time_hour increases, the temperature shows a generally increasing trend and the humidity increases as well.


## Problem 2

**Create a data frame**
```{r create_df}
df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = factor(c("a", "b", "c", "a", "b", "c","a", "b", "c","a"))
)
```

**Take the mean of each variable** 
```{r pull_mean}
mean_num = mean(pull(df, vec_numeric))
mean_logical = mean(pull(df, vec_logical))
mean_char = mean(pull(df, vec_char))
mean_factor = mean(pull(df, vec_factor))
```
Taking the mean works for the numeric variable and the logical variable, but it doesn't work for the character variable and the factor variable.\



**Convert to numeric variable**
```{r variable_convert, results = "hide"}
num_logical = as.numeric(pull(df, vec_logical))
num_char = as.numeric(pull(df, vec_char))
num_factor = as.numeric(pull(df, vec_factor))
```
The logical and factor variables are converted to numeric type successfully, while the character variable fails to be converted to be numeric (or is converted to NAs by coercion).
Yes.The mean function can only be applied to numeric and logical vectors.




