---
title: "p8105_hw1_sc5126.Rmd"
author: "Si Chen"
date: "2023-09-23"
output: github_document
---


## Problem 1

load dataset
```{r load_data}
library(moderndive)
library(ggplot2)
data("early_january_weather")
```


Description of the dataset:\
The variables in the dataset include `r colnames(early_january_weather)`. \
The highest temperature is `r max(early_january_weather$temp)` and the lowest temperature is `r min(early_january_weather$temp)`. The mean of humidity is `r mean(early_january_weather$humid)` and the mean of visibility is `r mean(early_january_weather$visib)`.\
There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns in the dataset.\
The mean temperature is `r mean(early_january_weather$temp)`.\






```{r plot_prob1}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_temp_time.png")
```
As the time_hour increases, the temperature shows a generally increasing trend and the humidity increases as well.







